Dike experiment

### 2022-12-16 manuscript.Rmd
Update manuscript

---
title: "Dike experiment"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: template_word.docx
csl: template-journal-of-vegetation-science.csl
bibliography: bibliography.bib
---

@@

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-1)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021]. During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-s1)). Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?  --> and a with an excavator the substrates were mixed <!--# Is that right?  --> and the plots prepared. The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016 ). The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <!--# check numbers  -->, respectively. The seeds were received from a commercial producer of autochtonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(fig:table-2))<!--# check  -->. The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:table-3)) <!--# More details and check  -->. The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.

We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates). The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-1)). The split plot was cuased by testing all 24 treatments on both sides of the dike. We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs. 30 cm). Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed. The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(fig:table-1)). The two seed mixture types were tested with two seeding densities (4 vs. 8 g m\^-2 ). The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964]. Establishment rates of species

@@

\## Table 1

@@

```{r table-1, fig.cap = "table_1"}
read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
  slice(-1) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(
    top = FALSE,
    values = read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>% slice(1)
    ) %>%
  fit_to_width(16.5, inc = 1L, max_iter = 20, unit = "cm")
```

@@

```{r table-2, fig.cap = "table_2"}
read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(top = FALSE, values = c("", "", "#", "#", "%", "%")) %>%
  autofit()
```

@@

@@

```{r figure-1, fig.cap = "figure-1"}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
```

@@

```{r figure-2, fig.cap = "figure-2"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r figure-3, fig.cap = "figure-3"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-4, fig.cap = "figure-4"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-5, fig.cap = "figure-5"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-6, fig.cap = "figure-6"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```

@@

```{r table-s1, fig.cap = "table-s1"}
read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
  autofit()
```

@@

```{r table-s2, fig.cap = "table-s2"}
knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))
```

>>>>

---
title: "Dike experiment"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  bookdown::word_document2:
    reference_docx: template_word.docx
csl: template-journal-of-vegetation-science.csl
bibliography: bibliography.bib
---

@@

The seed mixture-substrate combination were tested with an experiment on a dike of the River Danube in SE Germany, which was established in March 2018 (Figure \@ref(fig:figure-map)), 314 m above sea level (asl); WGS84 (lat/lon), 48.83895, 12.88412). The climate is temperate-suboceanic with a mean annual temperature of 8.4 °C and precipitation of 984 mm [@dwd2021]. During the study, three exceptionally dry years (2018--2020) occurred [@cdc2022temp; @cdc2022prec], and three minor floods which did not reach the plots [@lfu2021waterlevel,@lfu2021discharge] (Table \@ref(fig:table-flood-weather)). Regional sand (0--4 mm) was used to lean the substrate and the soil was taken from the dike <!--# Is that right?  --> and a with an excavator the substrates were mixed <!--# Is that right?  --> and the plots prepared. The target vegetation were lowland hay meadows (Arrhenatherion elatioris, CM01A) and calcareous grassland (Cirsio-Brachypodion pinnati, DA01B code of the EuroVegChecklist, @mucina2016 ). The species pool of hay meadows and calcareous grasslands consisted of 55 and 58 species <!--# check numbers  -->, respectively. The seeds were received from a commercial producer of autochtonous seeds. From the species pools, 20 species were randomly selected for each plot. The seed mixtures always contained seven grasses (60 wt% of total seed mixture), three legumes (5%) and ten herbs (35%) (Table \@ref(fig:table-seedmix))<!--# check  -->. The community-weighted means (CWM) of functional traits differed between the seed mixture types (Table \@ref(fig:table-3)) <!--# More details and check  -->. The management started with a cut without hay removal and a mowing height of 20 cm in August 2018, followed by 'normal' deep cuts with hay removal in July 2019 and 2020. In October 2018, Bromus hordeaceus was seeded as a nursery grass to provide safe sites under drought conditions.

We used 288 plots of the size 2.0 m × 2.0 m which were distributed over the north and south exposition of the dike and arranged in six blocks (= replicates). The experiment used a split plot design combined with randomized complete block design (Figure \@ref(fig:figure-map)). The split plot was cuased by testing all 24 treatments on both sides of the dike. We tested three substrates with 0%, 25% and 50% sand admixture and two soil depths (15 vs. 30 cm). Below the substrate, a drainage layer of 5 cm consisting of gravel (0--16 mm) was installed. The sand admixture changed the soil texture, increased the C/N ratio, but reduced the ratio of Calciumcarbonat, and hardly changed the pH (Table \@ref(fig:table-substrate)). The two seed mixture types were tested with two seeding densities (4 vs. 8 g m\^-2 ). The vegetation was surveyed in June or July 2018--2021 [@BraunBlanquet.1964]. Establishment rates of species

@@

## Table 1

@@

```{r table-substrate, fig.cap = "table_substrate"}
read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
  slice(-1) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(
    top = FALSE,
    values = read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>% slice(1)
    ) %>%
  autofit()
```

@@

```{r table-seedmix, fig.cap = "table_seedmix"}
read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(top = FALSE, values = c("", "", "#", "#", "%", "%")) %>%
  autofit()
```

@@

## Table 3

functional traits <!--# full description + table -->

```{r table-traits, fig.cap = "table_traits"}
read_csv(here::here("data", "raw", "data_raw_table_2.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  autofit()
```

@@

```{r figure-map, fig.cap = "figure-map"}
knitr::include_graphics(here::here("outputs", "figures", "figure_1_map_tmap_300dpi_8x11cm.tiff"))
```

@@

```{r figure-effects, fig.cap = "figure-effects"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_2_800dpi_16.5x5cm.tiff"))
```

@@

```{r figure-persistence, fig.cap = "figure-3"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_3_persistence_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-fcs, fig.cap = "figure-4"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_4_fcs_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-recovery, fig.cap = "figure-5"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_5_recovery_epred_800dpi_16.5x14cm.tiff"))
```

@@

```{r figure-nmds, fig.cap = "figure-6"}
#knitr::include_graphics(here::here("outputs", "figures", "figure_6_nmds_800dpi_16.5x16cm.tiff"))
```

@@

```{r table-flood-weather, fig.cap = "table-s1"}
read_csv(here::here("data", "raw", "data_raw_table_s1.csv")) %>%
  flextable() %>%
  bold(part = "header") %>%
  compose(part = "body", i = ~ Unit == "m3 s−1", j = "Unit", value = as_paragraph("m", as_sup("3"), " s", as_sup("−1"))) %>%
  autofit()
```

@@

```{r table-establishment, fig.cap = "table-s2"}
knitr::include_graphics(here::here("outputs", "tables", "table_a2_establishment.html"))
```
